Paper_analyses

### 2021-09-07 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c)

@@

  plots_paper$pupil_correlation+ p$graphstyle
```

@@

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  subset(!is.na(ground_valence_2))%>%
  group_by(ssid, stimIAPS,ground_valence_2)%>%

@@

#

pupil_arousal_findings$BIO_CDA.PhasicMax_ar <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

@@

@@

@@

@@

pca_res <- prcomp(clustering_agg_bonkers[1:55,c(25,24,20)], center = TRUE, scale. = TRUE)
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)

# plot_data$
ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
  geom_point(size = 2, alpha = .4)+
  # geom_text(aes(label= clustering_agg$stimDescription))+
  stat_ellipse(show.legend = TRUE)+
  ylab("Componet 2")+
  xlab("Component 1")+
  # scale_color_manual(values = c("red", "green", "blue"))+
  p$graphstyle+
  theme()

@@

clustering3$arousal
clustering_new$Cluster<- as.factor(clustering_new$Cluster)
cluster_lmers$arousal <- lmer(arousal ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering_new)

@@

# valence
cluster_lmers$valence <- lmer(valence ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering_new)

@@

>>>>

summary(pupil_arousal_findings$pupil_from_ar_vale)
plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c)

@@

  plots_paper$pupil_correlation+ p$graphstyle

summary(lmer(pup_basCor ~ (valence_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE)))

summary(lmer(pup_basCor ~ (arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE)))

summary(lmer(pup_basCor ~ (arousal_c+valence_c)
                                                      +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE)))

macthed_test$stimIAPS2<- as.character(macthed_test$stimIAPS2)
test_matchedM<- left_join( macthed_test, db_full4new_stim_screen_pupil_nopract,by = "stimIAPS2")

matchedPupiltest <- lmer(pup_basCor ~ (arousal_c*valence_c)
                                                      +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = test_matchedM%>%
                         subset(Group == "NT"))

matchedPupiltest

interactions::interact_plot(matchedPupiltest , pred =arousal_c  , modx =  valence_c)

swicth predictirs

```{r}
unique(db_full4new_stim_screen_pupil_nopract$ssid)

library(lmerTest)
pupil_arousal_findings$ar_from_val_pup <- lmer(arousal_c ~ valence_c*pup_basCor +
                                                    Mean_gray_z  +
                                                    (1 | ssid)+
                                                    (1|stimIAPS),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                        subset(Group == "NT"))
                        # subset(pupil_outlier == FALSE)%>%
                        # subset(arousal_outler == FALSE))

summary(pupil_arousal_findings$ar_from_val_pup)

interactions::interact_plot(pupil_arousal_findings$ar_from_val_pup, pred = valence_c, modx =  pup_basCor)

@@

test<- subset(db_full4new_stim_screen_pupil_nopract, 
                                    Group == "NT")

cor.test(test$arousal_c, test$valence_c)
?rmcorr::rmcorr
plot(rmcorr::rmcorr(participant = "stimIAPS2", measure1 = "arousal_c", measure2 = "valence_c", data = test))

plot(rmcorr::rmcorr(participant = "ssid", measure1 = "arousal_c", measure2 = "valence_c", data = test))

db_full4new_stim_screen_pupil_nopract%>%
  ggplot(aes(arousal_c, valence_c))+
  geom_point()

# pollu
db_full4new_stim_screen_pupil_nopract$valence_c_sq<- db_full4new_stim_screen_pupil_nopract$valence**2
polyyrelation<- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = db_full4new_stim_screen_pupil_nopract)
```

@@

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_valence_2))%>%
  group_by(ssid, stimIAPS,ground_valence_2)%>%

@@

# macthed test

```{r}
unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)

db_full4new_stim_screen_pupil_nopract_nt_304$stimIAPS2<- as.character(substr(db_full4new_stim_screen_pupil_nopract_nt_304$stimIAPS, 1,4))

nrow(db_full4new_stim_screen_pupil_nopract_nt_304)
nrow(testmatched_scr)
testmatched_scr<- left_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")

testmcthedscr <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = testmatched_scr)

summary(testmcthedscr)

anova(pupil_arousal_findings$arousal_phas_max)

interactions::interact_plot(testmcthedscr, pred = arousal_c, modx = valence_c)

```
pupil_arousal_findings$BIO_CDA.PhasicMax_ar <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

@@

semi matched dataset
```

@@

library(ggplot2)
library(reshape2)
library(data.table)
library(tidyr)
library(tidyverse)
?gather

db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
  subset(ssid!= "347")%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
  select(c(ssid, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
  gather(key, value, -ssid)%>%
  group_by(ssid, key, value)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(key, value))+
  geom_jitter(width = .1, alpha = .1)+
  geom_line(aes(group = ssid), se = F)+
  stat_summary(geom = 'pointrange')

@@

clustering_agg_JASP$valence_median_split<- if_else(clustering_agg_JASP$valence > median(clustering_agg_JASP$valence,na.rm = TRUE), "positive", "negative")

clustering_agg_JASP$ValenceMean_median_split <- if_else(clustering_agg_JASP$ValenceMean > median(clustering_agg_JASP$ValenceMean,na.rm = TRUE), "positive", "negative")

clustering_agg_JASP%>%
  mutate(abs_ar  = abs(arousal))%>%
  # ggplot(aes(valence_median_split, arousal))+
  ggpubr::ggboxplot(x = "valence_median_split", y = "abs_ar")+
  geom_point()

clustering_agg_JASP%>%
  mutate(abs_ar = abs(clustering_agg_JASP))
  # ggplot(aes(valence_median_split, arousal))+
  ggpubr::ggboxplot(x = "ValenceMean_median_split", y = "ArousalMean")+
  geom_point()+
  stat_summary(geom = 'pointrange')

write_csv(clustering_agg_JASP, "clustering_agg_JASP_newtomatch.csv")

library(readxl)
macthed_test <- read_excel("macthed_test.xlsx")
View(macthed_test)

macthed_test%>%
  # ggplot(aes(valence_median_split, arousal))+
  ggpubr::ggboxplot(x = "ValenceMean_median_split", y = "ArousalMean")+
  # geom_point()+
  stat_summary(geom = 'pointrange')
```

@@

pca_res <- prcomp(clustering_agg[,c(25,24,20)], center = TRUE, scale. = TRUE)
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = TRUE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)

# plot_data$
ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
  geom_point(size = 2, alpha = .4)+
  geom_text(aes(label= clustering_agg$stimDescription))+
  stat_ellipse(show.legend = TRUE)+
  ylab("Componet 2")+
  xlab("Component 1")+
  # scale_color_manual(values = c("red", "green", "blue"))+
  p$graphstyle+
  theme()

@@

clustering3$arousal
clustering_new$Cluster<- as.factor(clustering_new$Cluster)
cluster_lmers$arousal <- lmer(arousal ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS),
                             REML = FALSE,
                             data = clustering_new)

@@

# valence
cluster_lmers$valence <- lmer(valence ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS),
                             REML = FALSE,
                             data = clustering_new)

@@

clustering_new_agg<- clustering_new%>%
  subset(!is.na(Cluster))%>%
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
clustering_new_agg$Cluster<- factor(clustering_new_agg$Cluster)

clustering_new_agg
clusr_ar<- afex::aov_ez(id = "ssid",
             data = clustering_new_agg,
             dv = "arousal",
             within = "Cluster",
             between = NULL)

clustering_new_agg%>%
  ggplot(aes(Cluster, arousal))+
  geom_jitter(width = .2)+
  geom_boxplot()
emmeans::emmeans(clusr_ar, pairwise~Cluster, adjust = "bonf")

clusr_vl<- afex::aov_ez(id = "ssid",
             data = clustering_new_agg,
             dv = "valence",
             within = "Cluster",
             between = NULL)

emmeans::emmeans(clusr_vl, pairwise~Cluster, adjust = "bonf")
